Neural dialogue act recognition with transformer pre-training

### 2019-04-06 abstract.tex
experiments

\paragraph{Experiments.}
Our aim is to test the effectiveness of different utterance encoding strategies. 
\begin{enumerate}
  \item Average word embedding (word2vec, FastText)
  \item CNN (with/without word2vec initalization, with/without `freezing' the embeddings )
  \item BERT encoded sentences (with/without additional unsupervised pretraining)
  \item Average BERT word embeddings (?)
  \end{enumerate}

  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for DAR, additional information only present in natural dialogue data will be useful. Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models. \textbf{(How?)} For the datasets where no annotation for disfluencies is available, it can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.

  Furthermore PoS tags

>>>>

\paragraph{Experiments.}
Our aim is to test the effectiveness of different utterance encoding strategies. We investigate the following strategies:
\begin{enumerate}
  \item Averaging of word2vec/BERT word embedding
  \item Encoding utterances with CNN (with/without word2vec/BERT initalization, with/without `freezing' the embeddings)
  \item BERT encoded sentences (with/without additional unsupervised pretraining on full Switchboard corpus)
  \end{enumerate}

  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for DAR, additional information only present in natural dialogue data will be useful. In SWDA disfluencies are annotated and for the datasets where no annotation for disfluencies is available, they can be predicted from recognized speech \citep{hough2017joint,shalyminov2018multi}. We evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models and suggests the ways to include information about disfluencies in pre-trained models.

  % PoS tags?
